Wikipedia Text Mining and Entropy Analysis

### 2018-09-17 wiki_entropy.Rmd
Added Finnish, Korean and Arabic

def extract_texts(upper_bound):
	rs = ""
	for i in range(upper_bound):
		if i < 10:
			number = "0" + str(i)
		else:
			number = str(i)
		f = open("~/Documents/Labword/Joe/misc/text/AA/wiki_" + number, 'r')
		text = f.read()
		rs += text
	return rs

@@

text = extract_texts(99)
ky_df = get_sen_df(text)
```

@@

entropies <- map(6:12, ~get_entropies(.x, py$ky_df)) %>%
  bind_rows()

>>>>

def extract_texts(upper_bound):
	rs = ""
	for i in range(upper_bound):
		if i < 10:
			number = "0" + str(i)
		else:
			number = str(i)
		f = open("../misc/text/AA/wiki_" + number, 'r')
		text = f.read()
		rs += text
	return rs

@@

text = extract_texts(20)
ar_df = get_sen_df(text)
```

@@

entropies <- map(6:12, ~get_entropies(.x, py$ar_df)) %>%
  bind_rows()
